---
output:
  md_document:
    variant: markdown_github
---

[![Project Status: Active  The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)  
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.2.4-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange.svg?style=flat-square)](commits/develop)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)


LCSLCIS
--------

An R library to compute the longuest common sequences. It contains 2 functions: 

- **LCS**: Longest Common Sequence
- **LCIS**: Longest Common I Sequence

<br><br>

## Installation
The LCSLCIS library is not on CRAN yet. However you can easily install it from this github repository:
```{r}
#install.packages("devtools")
library(devtools) 
install_github("holtzy/LCSLCIS")
library(LCSLCIS)
```



## Basic example
Let's consider 2 lists of elements. Each element has a specific position in each list. We can build such a dataset and represent it in the following diagram:  

```{r}
o1 <- data.frame( 
	V1=c("g","h","c","f","e","d","m","q","r","a","b","n","o","p"), 
	V2=c(1.1,1.1,3.4,3.4,3.4,3.4,3.5,3.5,6.6,6.6,7.2,7.2,8,8)
	)
o2 <- data.frame( 
	V1=c("k","a","b","l","c","e","d","f","i","j","h","g"), 
	V2=c(0.1,1.2,1.2,4.2,4.2,5,5,5,5.3,5.3,6.7,6.7)
	)
```

The library provides a function that allows to visualize the relationship between these 2 lists.
```{r}
show_connection(o1, o2)
```


We can now try to find the biggest set of elements without having any mismatch in their order. This can be done using the `LCS` or the `LCIS` function. Here is an example using LCS:

```{r}
# run the LCS function
res <- LCS(o1,o2)

# The number of elements we can keep without order mismatch is 
res$LLCS

# The elements we can keep are:
res$LCS

# We can represent that on the diagram:
show_connection(o1, o2, tokeep=res$LCS)
```


## Applying to genetic maps
The LCSLCIS library provide 2 genetic maps of wheat as toy example. Load it with:
```{r}
data(geneticMap)
```

You can have a look to this 2 genetic maps doing:
```{r, eval=FALSE}
head(map1)
head(map2)
```

We need to reformat this map to have an expected input: 2 columns called V1 (item name) and V2 (item position)
```{r}
o1 <- map1 %>% filter(V0=="1A") %>% select(V1, V2) %>% arrange(V2)
o2 <- map2 %>% filter(V0=="1A") %>% select(V1, V2) %>% arrange(V2)
```

Let's have a look to the common items relationship:
```{r}
show_connection(o1, o2, showName=FALSE)
```

Let's run LCIS to keep a subset of markers with no crossing:
```{r}
res <- LCIS(o1,o2)
show_connection(o1, o2, tokeep=res$LCIS, showName=FALSE)
```


## Citing

If you find LCSLCSI useful, please cite:  
in press.



## Authors

Vincent Ranwez: [homepage](https://sites.google.com/site/ranwez/)
Other:








