---
output:
  md_document:
    variant: markdown_github
---

[![Project Status: Active  The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)  
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.2.4-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange.svg?style=flat-square)](commits/develop)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)


LCSLCIS
--------

An R library to compute the Longuest Common Subsequence between 2 lists of items.

## Abstract
Genetic maps order genetic markers along chromosomes. They are, for instance, extensively used in marker-assisted selection to accelerate breeding program. Even for the same species, people often have to deal with several alternative maps obtained using différent ordering methods or différent dataset, e.g. resulting from différent segregating populations. Having efficient tools to identify the consistency and discrepancy of alternative maps is thus essential to facilitate genetic map comparisons.  
We propose to encode genetic maps by bucket order, a kind of order, which takes into account the blur parts of the marker order while being an efficient data structure to achieve low complexity algorithms. We identify the **Longest Common Subsequences** of bucket orders to produce a strict consensus genetic map. The main result of this paper is an O(nlog(n)) procedure to identify the largest agreements between two bucket orders of n elements, hence providing an efficient solution to highlight discrepancies between two genetic maps.


<br><br>

## Installation
The LCSLCIS library is not on CRAN. However you can install it from this github repository:
```{r, warning=FALSE, message=FALSE}
library(devtools) 
install_github("holtzy/LCSLCIS")
library(LCSLCIS)
```



## Basic example
Let's consider 2 lists of items o1 and o2. Each item has a specific position in each list. Several items can have the same position. 
```{r}
o1 <- data.frame( 
	V1=c("g","h","c","f","e","d","m","q","r","a","b","n","o","p"), 
	V2=c(1.1,1.1,3.4,3.4,3.4,3.4,3.5,3.5,6.6,6.6,7.2,7.2,8,8)
	)
o2 <- data.frame( 
	V1=c("k","a","b","l","c","e","d","f","i","j","h","g"), 
	V2=c(0.1,1.2,1.2,4.2,4.2,5,5,5,5.3,5.3,6.7,6.7)
	)
```

The LCSLCIS package provides a `show_connection` function that allows to visualize the relationship between these 2 lists:
```{r}
show_connection(o1, o2)
```

We can find the Longest Common Subsequences (LCS) of bucket orders to produce a strict consensus list. This is done running the `LCS` function of the package:
```{r}
res <- LCS(o1,o2)
```

The `LCS` function returns a list. Several outputs are of interest:

- `res$LLCS` is the number of items in the LCS:
```{r}
res$LLCS
```
- `res$LCS` provides the items of the LCS:
```{r}
res$LCS
```
- It is straigth forward to plot only the items of the LCS:
```{r}
show_connection(o1, o2, tokeep=res$LCS)
```


## Applying to genetic maps
The LCSLCIS library provide 2 genetic maps of wheat as toy example. Load it with:
```{r}
data(geneticMap)
```

You can have a look to this 2 genetic maps doing:
```{r, eval=FALSE}
head(map1)
head(map2)
```

We need to reformat this map to have an expected input: 2 columns called V1 (item name) and V2 (item position)
```{r}
o1 <- map1 %>% filter(V0=="1A") %>% select(V1, V2) %>% arrange(V2)
o2 <- map2 %>% filter(V0=="1A") %>% select(V1, V2) %>% arrange(V2)
```

Let's have a look to the common items relationship:
```{r}
show_connection(o1, o2, showName=FALSE)
```

Let's run LCIS to keep a subset of markers with no crossing:
```{r}
res <- LCIS(o1,o2)
show_connection(o1, o2, tokeep=res$LCIS, showName=FALSE)
```


## Citing

If you find LCSLCSI useful, please cite: 
*Longest Common Subsequence of Bucket Order: Application to Genetic Map Comparison (In Press)*


## Authors

Lisa De Mattéo: [linkedin](https://www.linkedin.com/in/lisadematteo/)
Vincent Ranwez: [homepage](https://sites.google.com/site/ranwez/)
Sèverine Bérard: [homepage](http://www.pages-perso-severine-berard.univ-montp2.fr)









